\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation on forest district levels \\ \vspace{2ex} \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}

### 2018-02-27 Draft_Form/saerlp_article_master.tex
update 25_01_2018
update 25_01_2018 (begin Results)
update 03_02_2018
update 03_02_2018
update 04_02_2018
update 04_02_2018
update 07_02_2018
update 07_02_2018
update 09_02_2018
update 09_02_2018
update 11_02_2018
update 11_02_2018
update 12_02_2018
update 12_02_2018
update 13_02_2018
update 13_02_2018
update 15_02_2018
update 15_02_2018
update 27_02_2018
update 27_02_2018 (Alex review)

% \date{\vspace{-0.3cm} \large \today \vspace{1.1cm}}
\date{\vspace{-0.8ex}}
\title{\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex}
  \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}}
\subject{\vspace{-1.5cm} Article Draft \vspace{0.2cm} \vspace{-0.5cm}}

@@

% comment out to disable line-numbering:
%\usepackage{lineno}
%\linenumbers

@@

% reocurring terms:
\newcommand{\adjrsq}{adjusted $R^2$}
\newcommand{\rmsecv}{RMSE$_{cv}$}
\newcommand{\mha}{m$^3$/ha}
\newcommand{\var}{\mathbb{V}}
\newcommand{\EX}{\mathbb{E}}
\newcommand{\psynth}{\textit{PSYNTH}}
\newcommand{\psmall}{\textit{PSMALL}}
\newcommand{\extpsynth}{\textit{EXTPSYNTH}}

@@

\input{tex/Introduction(2)}\newpage\cleardoublepage

@@

%\input{tex/Results}\newpage\cleardoublepage

@@

%\input{tex/Discussion}\newpage\cleardoublepage

@@

%\input{tex/Conclusions}\newpage\cleardoublepage

@@

%\input{tex/Acknowledgements}\newpage\cleardoublepage

@@

%\input{tex/Appendices}\newpage\cleardoublepage

>>>>

% \date{\vspace{-0.3cm} \large \today \vspace{1.1cm}}
\date{\vspace{-0.8ex}}
\title{\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation on forest district levels \\ \vspace{2ex}
  \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}}
\subject{\vspace{-1.5cm} Article Draft \vspace{0.2cm} \vspace{-0.5cm}}

@@

% comment out to disable line-numbering:
\usepackage{lineno}
\linenumbers

@@

% reocurring terms:
\newcommand{\adjrsq}{adjusted $R^2$}
\newcommand{\rmsecv}{RMSE$_{cv}$}
\newcommand{\mha}{m$^3$/ha}
\newcommand{\var}{\mathbb{V}}
\newcommand{\EX}{\mathbb{E}}
\newcommand{\psynth}{PSYNTH}
\newcommand{\psmall}{PSMALL}
\newcommand{\extpsynth}{EXTPSYNTH}
\newcommand{\meanheight}{\textit{meanheight}}
\newcommand{\stddev}{\textit{stddev}}
\newcommand{\treespecies}{\textit{treespecies}}
\newcommand{\alsyear}{\textit{ALSyear}}

@@

\input{tex/Introduction(2)}% \newpage\cleardoublepage

@@

\input{tex/Results}\newpage\cleardoublepage

@@

\input{tex/Discussion}%\newpage\cleardoublepage

@@

\input{tex/Conclusions}% \newpage\cleardoublepage

@@

\input{tex/Acknowledgements}\newpage\cleardoublepage

@@

\input{tex/Appendices}\newpage\cleardoublepage

### 2018-02-27 Draft_Form/tex/Appendices.tex
update 27_02_2018
update 27_02_2018 (Alex review)

\noindent $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to equations \ref{eq:locdens_clust} and \ref{eq:globresids}. $\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (equ. \ref{eq:srs_est_clusters}).\par

@@

\noindent The \textit{relative} or \textit{normalized} RMSE is calculated by setting the absolute RMSE in relation to the estimated sample mean $\hat{\bar{Y}}_c$:

@@

\noindent Generally note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.

>>>>

\noindent $Y_c(x)$ and $\hat{Y}_{c}(x)$ are the predicted and observed local densities on the cluster level calculated according to Equations \ref{eq:locdens_clust} and \ref{eq:globresids}. $\hat{\bar{Y}}_c$ is the estimated sample mean corresponding to the weighted mean over all observed local densities on the cluster level (Eq. \ref{eq:srs_est_clusters}).\par

@@

\noindent The \textit{relative} or \textit{normalized} RMSE is calculated by dividing the RMSE by the estimated sample mean $\hat{\bar{Y}}_c$:

@@

\noindent Note that the weights $\frac{M(x)}{\bar{M_2}} \equiv 1$ if the number of plots per cluster is constant.

### 2018-02-27 Draft_Form/tex/Conclusions.tex
update 14_02_2018
update 14_02_2018
update 27_02_2018
update 27_02_2018 (Alex review)

The study led to two major conclusions: (1) the \extpsynth{} and \psmall{} estimator generally achieved substantially smaller estimation errors on the two investigated forest district levels compared to the SRS estimator. The demonstrated double-sampling procedure thus constitutes a major contribution to an increase in value of the existing German NFI data on the federal state level. However, it is not possible to conclude from our study results alone whether the realized error levels are already acceptable in order to support forest planning decisions. Thus, further investigations are necessary in close cooperation with the forest authorities. A first study will concentrate on testing the \extpsynth{} and \psmall{} confidence intervals as a validation source for the stand-wise inventories. (2) Despite the quality restrictions in the ALS data and the tree species map, the two data sources were found to be well suited to model the mean timber volume on plot and cluster level. With respect to frequently updated aerial canopy height models and tree species maps, it will thus be of hight interest to investigate the model and estimation accuracies that can be expected for future applications. In this framework, the incorporation of additional auxiliary data and the extension to change estimation seem the reasonable next steps to be explored towards an operational implementation of the demonstrated double-sampling procedure.

%The application of the design-unbiased \extpsynth{} and \psmall{} estimator should be preferred over synthetic estimations whenever possible, since they also account for the model inaccuracies and thus provide unbiased estimates as well as more realistic confidence intervals.
%
%
%
%
%We draw three major conclusions from our study: (1) our analyses strongly indicated that the acquisition of auxiliary data close to the date of the terrestrial survey is a key factor to achieve good model accuracies. Particularly for large-scale inventory applications, this requirement is often difficult to meet. In such cases, we consider that the proposed method of including quality information about the auxiliary data in a prediction model can be an effective technique for improving the prediction accuracy. Ongoing studies investigate whether this modelling technique can also lead to smaller estimation errors of design-based estimators. (2) Our study also indicated that the relationship between the field measured timber volume and remote-sensing derived height information is tree species specific. We expect that using the tree species information in a timber volume model would even lead to higher prediction accuracies when combined with explanatory variables that can further explain the variation within each tree species group, such as bioclimatic growing conditions, soil properties and stand density on the plot level. (3) We consider the demonstrated calibration technique to be a valuable method for future studies where an external tree species map (i.e. the map was not created for the specific study objective) is used in prediction models. The application of a calibration model can also be transferred to any error-prone explanatory variable and be a simple means to clean the data set from noise and thus increase the model accuracy.

% - CONCLIUSION: 
%   o transfer of the suggested procedure to FDI inventories: maybe possible to get qunatified data for stands with acceptable estimation errors? (would be of high interest)
%   o the decision wether the errors are acceptable cannot be answered here but (in our opinion) depend on the question whether ... decisions can be made based on the provided Confidence Intervals.
%   o in a next step, we will investigate whether the derived confidence intervals are sufficient to be used as a validation for the stand-wise inventories (Kuliesis et al.)

% - The existing German NFI data can provide substantially smaller estimation errors on forest district levels when used in the proposed double-sampling estimators. However, the question which errors are acceptable to support operational forest planning cannot be answered purely based on the absolute error values. In our opinion, it depends on the question whether the derived confidence intervals a) allow for more profound decisions between forest planning alternatives.

% - prefer model-assisted estimators to synthetic estimators if one can afford --> because design-unbiased, they take the model inaccuracies into account and thus provide unbiased point estimates and more realsitic confidence intervals.

>>>>

The study led to two major conclusions: (1) the \extpsynth{} and \psmall{} estimator generally achieved substantially smaller estimation errors on the two investigated forest district levels compared to the SRS estimator. The demonstrated double-sampling procedure thus constitutes a major contribution to an increase in value of the existing German NFI data on the federal state level. However, it is not possible to conclude from our study results alone whether the realized error levels are already sufficient enough in order to support forest planning decisions. Thus, further investigations are necessary in close cooperation with the forest authorities. A first study will concentrate on testing the \extpsynth{} and \psmall{} confidence intervals as a validation source for the stand-wise inventories. (2) Despite the quality restrictions in the ALS data and the tree species map, the two data sources were found to be well suited to model the mean timber volume on plot and cluster levels. With respect to frequently updated aerial canopy height models and tree species maps, it will thus be of interest to investigate the model and estimation performances that can be expected for future applications. In this framework, the incorporation of additional auxiliary data and the extension to change estimation seem the reasonable next steps to be explored towards an operational implementation of the demonstrated double-sampling procedure.

### 2018-02-27 Draft_Form/tex/Discussion.tex
update 27_02_2018
update 27_02_2018 (Alex review)

The aim of this study was to investigate the performance of design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany. It was of particular interest to gather information about the estimation error levels that can be realized using the German NFI data, characterized by low sampling intensities in the area of interests, as terrestrial phase information in the two-phase estimators. To address these research questions, we applied the simple random sampling (SRS), the pseudo-small (\psmall{}) and the extended pseudo-synthetic (\extpsynth{}) estimator for cluster sampling to 45 and 405 small area units in the German state of Rhineland-Palatinate.\par

Our study showed that on both small area levels, the \psmall{} and the \extpsynth{} estimator generally leads to a substantial reduction of the estimation errors produced by the SRS estimator. On the upper management level (FA districts), \psmall{} and \extpsynth{} allowed to provide estimation errors smaller than 5\% for 73\% of the small areas compared to only 17\% under the SRS estimator. This level of estimation accuracy could not be achieved on the subsequent management level (FR districts). The reason for this were primarily the substantially smaller terrestrial sample sizes. However, in most FR units (95\%), the estimation errors could be limited to 20\% compared to 40\% under SRS. A pairwise comparison of the confidence intervals revealed that the estimators did thereby not produce significantly different point estimates. The much smaller estimation errors of the \psynth{} estimator suggested that the neglection of the regression model accuracies in the small area units leads to overoptimistic estimation accuracies and confidence intervals. If possible, one should thus prefer the unbiased estimates of \psmall{} or \extpsynth{}.\par

@@

We were also able to empirically confirm that the \extpsynth{} estimator generally produces slightly smaller variances and estimation errors than the \psmall{}. This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero-mean-residual property of the \extpsynth{}. However, our analysis indicated that the difference between the two estimators are negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency. Furthermore, one or more clusters not entirely included in the small area unit did reassuringly not have a notable impact on the estimates of \extpsynth{}. This empirical evidence can however not be generalized to any application of \extpsynth{} under cluster sampling. It thus seems recommendable to calculate both \psmall{} and \extpsynth{}, and subsequently compare their results. If no suspicious deviations occur, we consider the \extpsynth{} as the estimator of choice.\par

@@

The auxiliary data used in our study were derived from two remote sensing sources, i.e. an ALS canopy height model and a tree species classification map. Likewise in many similar studies, the ALS mean canopy height proved to be the explanatory variable with highest predictive power. However, the large time-gaps of up to 10 years between the ALS acquisition and the terrestrial survey date caused a substantial introduction of artificial noise in the data. Whereas a stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity. As opposed to the ALS data, the availability of a country-wide tree species classification map has yet been unique among all German federal states. Whereas the study of \citet{hill2017a} already showed that the tree species information was able to improve the model accuracy, it has yet not been used to its full potential. One reason for this was the impossibility of a tree species individual modeling within each ALS acquisition year, which we consider to add further explanatory power. Another reason was the lack of available satellite data for classification in some parts of the country, which led to missingness in the inventory data and restricted 19 FR units to a simpler regression model. Promising steps with respect to more up-to-date canopy height information have already been made, as the topographic survey institution of RLP will from this year on provide a country-wide canopy height model derived from aerial imagery acquisitions. These campaigns will in the future be conducted in a two-year period and allow to derive canopy height information matching the dates of terrestrial forest inventories. A study of \citet{kirchhoefer2017} recently indicated that similar model accuracies for German NFI data can be achieved using such imagery-based canopy height models. Due to the improved coverage and repetition rate of the Sentinel-2 satellite, also the tree species classification map will in the future be updated each year. We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots. Thus, one could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which theoretically leads to a further decrease of the estimation errors. Previous studies of \citet{mandallaz2013b} however showed that given a reasonable large sample size of the first phase, the differences in the estimation error are usually small. With respect to the substantial improvements in the temporal synchronicity between auxiliary and terrestrial inventory data, we consider the demonstrated double-sampling approach also to be very efficient for change estimation \citep{massey2015b}.\par

>>>>

The aim of this study was to investigate the performance of design-based estimators for small area estimation of mean standing timber volume on two spatial forest management levels in Germany. It was of particular interest to gather information about the estimation error levels that can be attained using German NFI data that is characterized by low sampling intensities in the area of interests. To address these research questions, we applied the SRS, the \psmall{} and the \extpsynth{} estimators for cluster sampling to two forest management levels consisting of 45 and 405 small area units respectively in the German state of Rhineland-Palatinate.\par

Our study showed that on both small area levels, the \psmall{} and the \extpsynth{} estimators generally led to a substantial reduction in estimation error compared to the standard one-phase SRS estimator. On the upper management level (FA districts), \psmall{} and \extpsynth{} produced estimation errors smaller than 5\% for 73\% of the small areas compared to only 17\% under the SRS estimator. The same level of precision could not be achieved on the lower management level (FR districts) primarily due to substantially smaller terrestrial sample sizes. The reason for this were primarily the substantially smaller terrestrial sample sizes. However, in 95\% of the FR units, the estimation errors could be limited to 20\% compared to 40\% under SRS. A pairwise comparison of the confidence intervals revealed that the estimators did not produce significantly different point estimates. The much smaller estimation errors of the \psynth{} estimator 
reflected the fact that it does not try to correct for potential bias in the point estimate which can lead to overly optimistic estimation errors and confidence intervals. One should thus prefer the unbiased estimates of \psmall{} or \extpsynth{}.\par

@@

We were also able to empirically confirm that the \extpsynth{} estimator generally produces slightly smaller variances and estimation errors than the \psmall{}. This is most probably caused by marginally smaller model residuals due to the intercept adjustment to the terrestrial data in the small area unit, which is primarily a means to ensure the zero-mean-residual property of the \extpsynth{}. However, our analysis indicated that the difference between the two estimators is negligible for sample sizes $\geq$ 10 due to their asymptotic equivalency. Furthermore, one or more clusters not entirely included in the small area unit did not have a notable impact on the estimates of \extpsynth{} when the terrestrial sample size was more than 6. However, there was a slight but statistically significant tendency to be over-optimistic for sample sizes between 4 and 6. More empirical evidence must be gathered before generalizing this as a rule of thumb for the application of the \extpsynth{} under cluster sampling. It thus seems recommendable to calculate both \psmall{} and \extpsynth{}, and subsequently compare their results. If no suspicious deviations occur, we consider the \extpsynth{} as the estimator of choice.\par

@@

The auxiliary data used in our study were derived from two remote sensing sources, i.e. an ALS canopy height model and a tree species classification map. Likewise in many similar studies, the ALS mean canopy height proved to be the explanatory variable with highest predictive power. However, the large time-gaps of up to 10 years between the ALS acquisition and the terrestrial survey date caused the substantial introduction of artificial noise in the data. Whereas a post-stratification to the ALS acquisition years was an effective means to counteract the implied residual inflation, several leverage points were unambiguously caused by the temporal asynchronicity. As opposed to the ALS data, the availability of a country-wide tree species classification map has yet been unique among all German federal states. Whereas the study of \citet{hill2017a} already showed that the tree species information was able to improve the model fit, it has yet not been used to its full potential. One reason for this was the impossibility of modeling individual tree species within each ALS acquisition year, which would add further explanatory power. Another reason was the lack of available satellite data for classification in some parts of the country, which led to missing values in the inventory data and restricted 19 FR units to a simpler regression model. Promising steps with respect to more up-to-date canopy height information have already been made, as the topographic survey institution of RLP will from this year on provide a country-wide canopy height model derived from aerial imagery acquisitions. These campaigns will in the future be conducted in a two-year period and allow to derive canopy height information matching the dates of terrestrial forest inventories. A study of \citet{kirchhoefer2017} recently indicated that similar model performance for German NFI data can be achieved using such imagery-based canopy height models. Due to the improved coverage and repetition rate of the Sentinel-2 satellite \citep{sentinel2}, the tree species classification map will in the future be updated each year. We consider these alternative auxiliary data sources to also solve the problem of missing explanatory variables at inventory plots. One could also make use of the exhaustive information within the two-phase estimators by using the true the auxiliary means \citep{mandallaz2013a, mandallaz2013b}, which could further decrease of the estimation errors. Previous studies of \citet{mandallaz2013b} however showed that given a reasonable large sample size of the first phase, the differences in the estimation error are usually small. With respect to the substantial improvements in the temporal synchronicity between auxiliary and terrestrial inventory data, we consider the demonstrated double-sampling approach also to be very efficient for change estimation \citep{massey2015b}.\par

### 2018-02-27 Draft_Form/tex/Introduction(2).tex
update 27_02_2018
update 27_02_2018 (Alex review)

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germanys forest over time. The NFI thereby has to satisfy various information needs and amongst others reports to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. At the current time, the inventory design of the German NFI solely rests upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany. As this implies covering a large area of 114'191 ha \citep{bwi3}, the sample size has been chosen according to satisfy high estimation accuracies for forest attributes on the national and federal state level. This however leads to very low sampling intensities and consequently, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated in operational forest planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to base their regional management strategies on quantitative and accurate information \citep{bockmann1998}. However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}. One method which has proven to be efficient is double-or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}. Double sampling incorporates inexpensive auxiliary information and can be used to either increase estimation precision under given terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size. A double sampling for stratification procedure has e.g. been used in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} lately illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Recent studies have lately extended double-sampling to triple-sampling estimation methods using auxiliary information in two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. An other example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

Two-phase and three-phase samplings techniques have also been used in the service of small area estimation (SAE). SAE techniques particular address the situation where the number of samples within a subunit, so-called small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit. A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics. A commonly applied SAE method is thereby known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not available in the small area. The statistical models are thereby often developed by "borrowing strength" from data outside the small area. There are numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, and most of the studies use unit-level models, i.e. the statistical models are fitted using data from inventory plots. Especially unit-level models for timber volume estimation under the use of various remote sensing data have been intensively investigated with respect to timber volume prediction \citep{koch2010, naesset2014inmaltamo}. There are also few studies that have investigated area level-models, where the auxiliary information is only provided on the SA-level \citep{magnussen2017}. Some studies have illustrated that even NFI data of low sampling densities can be used in small area estimation procedures to provide estimations of acceptable accuracy on much smaller management levels. One example is \citet{breidenbach2012} who used data from the Norwegian NFI for SAE estimations of standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35. Estimation errors under the applied model-based and design-based SAE estimators turned to be markedly smaller than achieved under simple random sampling (SRS). Another example is \citet{magnussen2014} who recently used the Swiss NFI data for SAE estimation of timber volume within 108 Swiss forest districts with sample sizes between 9 and 206. Despite these promising results, a similar study in Germany using the German NFI data for SAE estimation has not yet been conducted.\par

The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels when incorporated in small area estimation procedures. We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}. Auxiliary data were obtained from a countrywide airborne Laser scanning (ALS) canopy height model (CHM) and a tree species classification map and used for regression within tree species strata. The estimation accuracies were compared to those achieved under SRS sampling. The chosen double-sampling estimators were favoured for several reasons: \textbf{(i)} the design-based frame considerably relaxes requirements on the regression model which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can consider \textit{non-exhaustive}, i.e. non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for the design-dependency of the regression coefficients on the sample (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals. The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par

>>>>

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time. The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany. In order to cover a large area of 114'191 ha \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels. However, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgments from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}. However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}. One method which has proven to be efficient is double- or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}. Double sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size. Double-sampling procedures have already been used for stratification in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Recent studies have extended double-sampling to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

Two-phase and three-phase samplings techniques have also been applied to small area estimation (SAE). SAE techniques address the situation where the number of samples within a subunit, or small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit. A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics. One such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area. These models are trained using data from outside the small area in order to "borrow strength" from areas where information is available. Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e. the inventory plot is the unit of the response variable in the training data used for the model fit. Such unit-level models have been intensively investigated for timber volume estimation using various remote sensing auxiliary data \citep{koch2010, naesset2014inmaltamo}. Other studies have investigated area-level models, where the auxiliary information is only provided on the SA level \citep{magnussen2017}. Some studies have illustrated that even NFI data derived under low sampling densities can still be used to provide acceptable precision of small area estimates on much smaller management levels. One example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35. The estimation errors under the applied model-based and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator. Another example is \citet{magnussen2014} who recently used the Swiss NFI data to estimate timber volume within 108 Swiss forest districts with sample sizes between 9 and 206. Similar studies using German NFI data for small area estimation have been lacking.\par

The aim of this study was to investigate whether the German NFI data can provide acceptable estimation precision on two forest district levels using the latest small area estimation procedures. We therefore conducted a study in the German federal state Rhineland-Palatinate where we extended the German NFI to a double-sampling design and applied three types of design-based small area regression estimators in order to derive point and variance estimates of mean standing timber volume for 45 and 405 forest districts respectively. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a, mandallaz2013b}. Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata. The estimation precisions were compared to those obtained by the standard one-phase estimator for cluster sampling under simple random sampling. The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e. non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust to heteroscedasticity of the model residuals. The results from this study were considered to provide valuable information whether the suggested procedure might be a cost-saving alternative to a regional FDI.\par
